Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-12-07 prop_letter_ajhs.tex
prop_letter_ajhs.tex Resolving SUGGEST TEXT #3....

\begin{suggest}{\yutsung}{3}
A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current state of the quantum
system.  Specifically, for each mixed states $\rho =
\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j >
0$, and $\sum_{j=1}^{N}q_{j}=1$, the Born rule
induces a probability measure~$\muB_{\rho}$ defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}
\melem{\phi_{j}}{P}{\phi_{j}}$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
\end{suggest}
\begin{suggest}{\andy}{3}
If all the conditions are satisfied, and one knows all the
  $\ket{\phi_j} = \sum_{k=1}^{d}\alpha_{k}\ket{k}$ representing
the current state $\rho$ of the quantum system, then a conventional
probability measure can easily be
constructed~\citep{Born1983bibTeX,Mermin2007,Jaeger2007},  taking the 
form
\[ \muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}  q_{j}\muB_{\phi_{j}}\left(P\right) \ . \]
\end{suggest}
A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current state of the quantum
system.  Specifically, for each pure normalized quantum
state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
$\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
generalizes to mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
induces a probability measure $\muB_{\rho}$ defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

>>>>

A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current pure state of the quantum
system.  Specifically, for each pure normalized quantum
state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
$\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
generalizes to mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
induces a probability measure $\muB_{\rho}$ defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
